\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed,tabularx,array}
\usepackage{tocloft}
\usepackage{tgpagella}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[nodayofweek]{datetime}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
%-----------------------------------------------------------

\setlength{\outerbordwidth}{0pt}  % Width of border outside of title bars
\definecolor{shadecolor}{rgb}{0.9, 0.9, 0.98}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{rgb}{0.9, 0.9, 0.98}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.in}

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\textcolor{gray}{\textit{\thepage\ of \pageref{LastPage}}}}
\fancyfoot[L]{\textcolor{gray}{\textit{Curriculum Vitae}}}
\fancyfoot[C]{\textcolor{gray}{\textit{\shortdate\today}}}
%-----------------------------------------------------------
%Custom commands

\newcommand{\resitem}[1]{\item[$-$] #1 \vspace{-7pt}}

\newcommand{\resheading}[1]{\vspace{-5pt}
	\parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
		\begin{shaded}
			\setlength{\fboxrule}{0pt}\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large \textbf{\textsc{#1}}} \vphantom{p\^{E}}}}}}
		\end{shaded}
	}\vspace{-5pt}
}

\newcommand{\resheadingfirst}[1]{\vspace{0pt}
	\parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
		\begin{shaded}
			\setlength{\fboxrule}{0pt}\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
		\end{shaded}
	}\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{7in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		{#3} & {#4} \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
	\fontencoding{T1}
	
	\begin{tabularx}{7in}{Xr}
		\textbf{\Large Yiping Wang} & {\href{https://yiping.wang.vision}{{\fontfamily{qcr}\selectfont yiping.wang.vision}}} \\
		{\fontfamily{qcr}\selectfont \href{mailto:yipingwang@uvic.ca}{yipingwang@uvic.ca}} & {\faGithub} {\href{https://www.github.com/yiping-wang}{\fontfamily{qcr}\selectfont /yiping-wang}} \\
	\end{tabularx}
	\par\noindent\rule{\textwidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheadingfirst{Education}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\ressubheading{\href{https://www.uvic.ca/engineering/computerscience/index.php}{University of Victoria}}{Victoria, BC, Canada}{\textit{Honours Bachelor of Science} | \textit{Co-op}}{Sept. 2017 -- Present}
	
	\begin{itemize}
		\resitem{Major in Computer Science and Minor in Electrical Engineering.}
		\resitem{Cumulative GPA: 8.50 / 9.00}
		\resitem{Expected Apr. 2021}
	\end{itemize}
	
	\ressubheading{\href{http://ias.szu.edu.cn}{Institute for Advanced Study, Shenzhen University}}{Shenzhen, Guangdong, China}{\textit{Bachelor of Science}}{Sept. 2015 -- Jun. 2017}
	
	\begin{itemize}
		\resitem{Major in Physics and Biology.}
		\resitem{Cumulative GPA: 3.76 / 4.00}
		\resitem{Credits towards H.B.Sc. at the University of Victoria.}
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Research Interests}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Computer Vision \textbullet{} Medical Image Processing \textbullet{} Deep Learning
	
	I aim to combine deep learning and medical image processing to obtain expert diagnostic result as well as boost diagnostic accuracy. My ultimate goal is to predict disease before it happens. 
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Research Experience}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\ressubheading{\href{https://vision.uvic.ca}{Visual Computing Group | University of Victoria}}{Victoria, BC, Canada}{\textit{Undergraduate Research Assistant}}{May 2019 -- Aug. 2019}
	
	\begin{itemize}
		\resitem{TBD.}
	\end{itemize}
	
	\ressubheading{\href{https://cs.uwaterloo.ca/future-graduate-students/uroc}{Undergraduate Research Opportunities Conference}}{Waterloo, ON, Canada}{\textit{Attendee}}{Sept. 27 2018 -- Sept. 30 2018}
	
	\begin{itemize}
		\resitem{Fully funded workshop for top undergraduate students from North America to discover what graduate studies is like by working alongside faculty and current graduate students on mini-research projects and other activities at the University of Waterloo.}
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Industrial Experience}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\ressubheading{\href{https://www.encorefx.com}{EncoreFX}}{Victoria, BC, Canada}{\textit{Software Developer Co-op}}{Sept. 2018 -- Dec. 2018}
	
	\begin{itemize}
		\resitem{Developed an online Foreign Exchange Trading and Payment platform, EncoreFX Express, using Angular and C\# ASP.NET Core framework.}
		\resitem{Created user features and interfaces for facilitating interactions, which involves designing, developing, and testing new Angular components on the front-end, as well as building and updating new RESTful API on the back-end.}
		\resitem{Improved unit testing coverage using Jasmine, developed a Selenium test suite and researched in preventing Cross-Site Request Forgery and Cross-Site Scripting.}
	\end{itemize}
	
	\ressubheading{\href{https://kinsol.io}{Kinsol}}{Victoria, BC, Canada}{\textit{Software Developer Co-op}}{May 2018 -- Aug. 2018}
	
	\begin{itemize}
		\resitem{Developed several responsive chatbot applications using Python Flask framework, JavaScript ES6, jQuery, and Bootstrap framework.}
		\resitem{Improved Deep Neural Networks through hyper-parameter tuning, regularization and optimization for the chatbot team.}
		\resitem{Implemented the methods which detect and recognize different objects using OpenCV in Python for the traffic analysis team.}
	\end{itemize}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Projects}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{center} \vspace{-5pt}
		\begin{tabular}{m{10cm} >{\centering\arraybackslash}m{5cm} >{\centering\arraybackslash}m{2cm}} 
			\toprule
			{Project Title} & {Keywords} & {Report / Demo} \\ 
			\midrule
			\multirow{2}{*}{End-to-End Facial Expression Modifier} & Conditional GAN & {\href{https://drive.google.com/file/d/1XyAWn8jRRZzFj3G4Rd6Qv-b85v7mBodk/view?usp=sharing}{\faCloudDownload}} \\
			& Style Transfer & \\ 
			\hline
			\vspace{5pt}
			\multirow{2}{*}{\parbox{10cm}{Segmentation of Overlapping Cervical Cells by Joint Level Set Method}} & Level Set Method & {\href{https://drive.google.com/file/d/15seENaFC46H68YfpHWCDM-wuyLNIhuWC/view?usp=sharing}{\faCloudDownload}}\\
			& Segmentation & \\
			%\multirow{2}{*}{Strikers} & ST & Alan Smith \\
			% & ST & Mark Viduka \\
			%    11 & 0.598  & -0.597 \\ \bottomrule
			\bottomrule
		\end{tabular}
	\end{center}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Selected Course History}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{center} \vspace{-5pt}
		\begin{tabular}{m{10cm} >{\centering\arraybackslash}m{2cm} >{\centering\arraybackslash}m{5cm}}
			\toprule
			Course Name    & Grade & Instructor\\
			\midrule
			Deep Learning for Computer Vision  & A+ (94\%) & Kwang Moo Yi \\
			Medical Image Processing       & A+ (95\%)     & Alexandra Branzan Albu \\
			Introduction to Artificial Intelligence       & A+ (90\%)      & Alex Thomo      \\
			Introduction to Computer Graphics & A+ (95\%)      & Li Ji       \\
			\bottomrule
		\end{tabular}
	\end{center}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Awards \& Scholarships}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\textbf{Associate with the Institute for Advanced Study, Shenzhen University}
	\begin{itemize}\vspace{-8pt}
		\resitem{Outstanding Innovative Talent (First Prize, 2017)}
		\resitem{Excellent Student to Academic Performance (Second Prize, 2017)}
		\resitem{Huaqiang Entrance Scholarship (Second Prize, 2015)}
	\end{itemize}
	
	%Z%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\resheading{Professional Development}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\textbf{Online Courses through Coursera}
	%\begin{itemize}
	%	\resitem{Deep Learning Specialization}
	%	    \resitem{Data Structure and Algorithms Specialization}
	%	\resitem{C\# Programming for Unity Game Development Specialization}
	%\end{itemize}
	
	%\textbf{Online Courses through edX}
	%\begin{itemize}
	%	\resitem{Professional Android Developer MicroMasters}
	%	\resitem{Virtual Reality (VR) App Development Professional Certificate}
	%    \resitem{AWS Developer: Building on AWS}
	%\end{itemize}
	
\end{document}


