\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed,tabularx,array}
\usepackage{tocloft}
\usepackage{tgpagella}
\usepackage[english]{babel}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[nodayofweek]{datetime}
\usepackage{siunitx}
\usepackage{amsfonts}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage[super]{nth}
%-----------------------------------------------------------

\setlength{\outerbordwidth}{0pt}  % Width of border outside of title bars
\definecolor{shadecolor}{rgb}{0.9, 0.9, 0.98}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{rgb}{0.9, 0.9, 0.98}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup

\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.5in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.in}

\renewcommand{\headrulewidth}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[R]{\textcolor{gray}{\textit{\thepage\ of \pageref{LastPage}}}}
\fancyfoot[L]{\textcolor{gray}{\textit{Curriculum Vitae}}}
\fancyfoot[C]{\textcolor{gray}{\textit{\shortdate\today}}}
%-----------------------------------------------------------
%Custom commands

\newcommand{\resitem}[1]{\item[$-$] #1 \vspace{-7pt}}

\newcommand{\resheading}[1]{\vspace{-5pt}
	\parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
		\begin{shaded}
			\setlength{\fboxrule}{0pt}\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large \textbf{\textsc{#1}}} \vphantom{p\^{E}}}}}}
		\end{shaded}
	}\vspace{-5pt}
}

\newcommand{\resheadingfirst}[1]{\vspace{0pt}
	\parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
		\begin{shaded}
			\setlength{\fboxrule}{0pt}\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
		\end{shaded}
	}\vspace{-5pt}
}
\newcommand{\ressubheading}[4]{
	\begin{tabular*}{7in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		{#3} & {#4} \\
	\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}
	\fontencoding{T1}
	
	\begin{tabularx}{7in}{Xr}
		\textbf{\Large Yiping Wang} & {\href{https://yiping.wang.vision}{{\fontfamily{qcr}\selectfont yiping.wang.vision}}} \\
		{\fontfamily{qcr}\selectfont \href{mailto:yipingwang@uvic.ca}{yipingwang@uvic.ca}} & {\faGithub} {\href{https://www.github.com/yiping-wang}{\fontfamily{qcr}\selectfont /yiping-wang}} \\
	\end{tabularx}
	\par\noindent\rule{\textwidth}{1pt}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheadingfirst{Education}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	
	\ressubheading{\href{https://www.uvic.ca/engineering/computerscience/index.php}{University of Victoria}}{Victoria, BC, Canada}{\textit{Honours Bachelor of Science} | \textit{Co-op}}{Sept. 2017 -- Present}
	\begin{itemize}
		\resitem{Major in Computer Science and Minor in Electrical Engineering.}
		\resitem{Cumulative GPA: 8.42 / 9.00 or 90.11\%}
		\resitem{Expected Apr. 2021}
	\end{itemize}
	
	\ressubheading{\href{http://ias.szu.edu.cn}{Institute for Advanced Study, Shenzhen University}}{Shenzhen, Guangdong, China}{\textit{Bachelor of Science}}{Sept. 2015 -- Jun. 2017}
	\begin{itemize}
		\resitem{Major in Physics and Biology.}
		\resitem{Cumulative GPA: 3.76 / 4.00}
		\resitem{Transferred to the University of Victoria.}
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Research Interests}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\centerline{Computer Vision \textbullet{} Medical Image Processing \textbullet{} Machine Learning}
	My interest and enthusiasm for Computer Vision, Medical Image Processing and Machine Learning. I explore how to use medical image data and machine learning to help doctors make decisions. More and more studies show that we can predict disease before it happens by processing and analyzing medical images using machine learning. I am broadly interested in machine learning for improving lesion detection and classification, anatomical structure segmentation and quantification, cancer diagnosis and therapy. In a nutshell, I study and apply computer vision and machine learning for medical imaging. 
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Research Experience}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		\ressubheading{\href{http://www.bccancer.bc.ca/}{Jack Bell Research Centre | BC Cancer}}{Vancouver, BC, Canada}{\textit{Research Co-op}}{Sept. 2019 -- Present}
	\begin{itemize}
		\resitem{Research and Development of Deep Learning and Medical Image Processing tools for the analysis of pathology images.}
		\resitem{Development of web applications for the annotation of pathology images.}
		\resitem{Supervised by Prof. Ali Bashashati}
	\end{itemize}
	
	\ressubheading{\href{https://vision.uvic.ca}{Visual Computing Group | University of Victoria}}{Victoria, BC, Canada}{\textit{Research Intern}}{May 2019 -- Aug. 2019}
	\begin{itemize}
		\resitem{Research and development of a deep learning algorithm for automated detection and segmentation of liver tumour in pathology images using PyTorch. }
		\resitem{Research and development of a threshold-based algorithm for automated detection and segmentation of tumor area in PET Scan.}
		\resitem{Supervised by Prof. Kwang Moo Yi.}
	\end{itemize}
	
	\ressubheading{\href{https://uwaterloo.ca/mathematics-undergraduate-research-conference/}{Waterloo Mathematics Undergraduate Research Conference}}{Waterloo, ON, Canada}{\textit{Attendee}}{\nth{27} Sept. 2019 -- \nth{29} Sept. 2019}
	\begin{itemize}
		\resitem{Meet leaders in mathematical, computer and statistical sciences at a two-day, all-expenses-paid conference hosted by the Faculty of Mathematics at the University of Waterloo.}
	\end{itemize}
	
	\ressubheading{\href{https://cs.uwaterloo.ca/future-graduate-students/uroc}{Undergraduate Research Opportunities Conference}}{Waterloo, ON, Canada}{\textit{Attendee}}{\nth{27} Sept. 2018 -- \nth{30} Sept. 2018}
	\begin{itemize}
		\resitem{Fully funded workshop for top undergraduate students from North America to discover what graduate studies is like by working alongside faculty and current graduate students on mini-research projects and other activities at the University of Waterloo.}
	\end{itemize}
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Industry Experience}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\ressubheading{\href{https://www.encorefx.com}{EncoreFX}}{Victoria, BC, Canada}{\textit{Software Developer Co-op}}{Sept. 2018 -- Dec. 2018}
	\begin{itemize}
		\resitem{Developed an online Foreign Exchange Trading and Payment platform, EncoreFX Express, using Angular and C\# ASP.NET Core framework.}
		\resitem{Created user features and interfaces for facilitating interactions, which involves designing, developing, and testing new Angular components on the front-end, as well as building and updating new RESTful API on the back-end.}
		\resitem{Improved unit testing coverage using Jasmine, developed a Selenium test suite and researched in preventing Cross-Site Request Forgery and Cross-Site Scripting.}
	\end{itemize}
	
	\ressubheading{\href{https://kinsol.io}{Kinsol}}{Victoria, BC, Canada}{\textit{Software Developer Co-op}}{May 2018 -- Aug. 2018}
	\begin{itemize}
		\resitem{Developed several responsive chatbot applications using Python Flask framework, JavaScript ES6, jQuery, and Bootstrap framework.}
		\resitem{Improved Deep Neural Networks through hyper-parameter tuning, regularization and optimization for the chatbot team.}
		\resitem{Implemented methods which detect and recognize different objects using OpenCV in Python for the traffic analysis team.}
	\end{itemize}
	
	
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Projects}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\begin{center} \vspace{-5pt}
		\begin{tabular}{m{10cm} >{\centering\arraybackslash}m{5cm} >{\centering\arraybackslash}m{2cm}} 
			\toprule
			{Project Title} & {Keywords} & {Report} \\ 
			\midrule
			\multirow{3}{*}{End-to-End Facial Expression Modifier} & Conditional GAN & \\
			& Style Transfer & {\href{https://drive.google.com/file/d/1XyAWn8jRRZzFj3G4Rd6Qv-b85v7mBodk/view?usp=sharing}{\faCloudDownload}} \\ 
			& Wasserstein GAN & \\
			\hline
			\vspace{5pt}
			\multirow{3}{*}{\parbox{10cm}{Segmentation of Overlapping Cervical Cells by Joint Level Set Method}} & Level Set Method & \\
			& Segmentation & {\href{https://drive.google.com/file/d/15seENaFC46H68YfpHWCDM-wuyLNIhuWC/view?usp=sharing}{\faCloudDownload}} \\
			& Pap Smear Image Analysis & \\
			%\multirow{2}{*}{Strikers} & ST & Alan Smith \\
			% & ST & Mark Viduka \\
			%    11 & 0.598  & -0.597 \\ \bottomrule
			\bottomrule
		\end{tabular}
	\end{center}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Selected Course History}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\textbf{Associate with the University of Victoria}
	\begin{center} \vspace{-5pt}
		\begin{tabular}{m{10cm} >{\centering\arraybackslash}m{2cm} >{\centering\arraybackslash}m{5cm}}
			\toprule
			Course Name    & Grade & Instructor\\
			\midrule
			Deep Learning for Computer Vision  & A+ (94\%) & Kwang Moo Yi \\
			Medical Image Processing       & A+ (95\%)     & Alexandra Branzan Albu \\
			Optimization for Machine Learning & A+ (93\%)      & Wu-Sheng Lu   \\
			Introduction to Artificial Intelligence       & A+ (90\%)      & Alex Thomo      \\
			Introduction to Computer Graphics & A+ (95\%)      & Li Ji       \\
			\bottomrule
		\end{tabular}
	\end{center}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\resheading{Awards \& Scholarships}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\textbf{Associate with the Institute for Advanced Study, Shenzhen University}
	\begin{itemize}\vspace{-8pt}
		\resitem{Outstanding Innovative Talent (First Prize, 2017)}
		\resitem{Excellent Student to Academic Performance (Second Prize, 2017)}
		\resitem{Huaqiang Entrance Scholarship (Second Prize, 2015)}
	\end{itemize}
	
	
	%Z%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\resheading{Professional Development}
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%\textbf{Online Courses through Coursera}
	%\begin{itemize}
	%	\resitem{Deep Learning Specialization}
	%	    \resitem{Data Structure and Algorithms Specialization}
	%	\resitem{C\# Programming for Unity Game Development Specialization}
	%\end{itemize}
	
	%\textbf{Online Courses through edX}
	%\begin{itemize}
	%	\resitem{Professional Android Developer MicroMasters}
	%	\resitem{Virtual Reality (VR) App Development Professional Certificate}
	%    \resitem{AWS Developer: Building on AWS}
	%\end{itemize}
	
\end{document}